\chapter{Introduction}

\section{Background}

Each year, Santa Claus hosts a security conference (\href{https://kringlecon.com/}{Kringlecon}) in various locations around North Pole.
As part of the employee benefits in Whoville Pentest Boutique \footnote{Registered with Better Bugs Bureau.},
Grinch and Cindy Lou attended.

Following a really long day attending various talks and talking with vendors,
Grinch and Cindy Lou headed back to their hotel. The only available hotel was
Serverland Security Hotel \footnote{Not to be confused with SSH.}. Although it was getting late,
the discussions drifted away from talks

- Grinch, I don't know if you noticed, Santa seemed a bit off.

- Yeah, I didn't want to bring this up because, you know, of my past.
Not only he seemed a bit off, he was always repeating the same stuff. If I didn't
know any better, I'd consider him rude.

- I have a strange feeling but I think we should investigate further. Let's get to bed and start fresh tomorrow.

- Sounds like a plan.


\subsection{Note of the Whoville Pentest Boutique Board}
Due to COVID, employees of Whoville Pentest Boutique are not allowed to attend any conferences.
Additionally, we praise ourselves on keeping everything open. The report and all tools/solutions are also hosted \href{https://github.com/frite/kringlecon-2020}{here}.
Also, Grinch it came to my attention that since the lockdown, you were watching your screen, mumbling about boring series on Netflux. For the last time, those are teleconferences.
