\chapter{Objective 11a}

Grinch was swiftly booted out of Santa's office, so he returned back as Santa.
{\color{codegreen}Tinsel Upatree} mentioned briefly that Jack Frost has probably changed his score.
Grinch laughed, after all, they already had all the hints from solving that snowball machine thing.
This couldn't be harder. His approach would be the same. Get all nonces, feed them into his generator until they become synced and spit the next number.
He decided to verify the blockchain and print the nonces.

\begin{minted}{python}
with open('official_public.pem', 'rb') as fh:
        official_public_key = RSA.importKey(fh.read())
        c2 = Chain(load=True, filename='blockchain.dat')
        print('C2: Block chain verify: %s' % (c2.verify_chain(official_public_key, previous_hash='c6e2e6ecb785e7132c8003ab5aaba88d')))
        for block in c2.blocks:
            print (block.nonce)
\end{minted}

Now that he had the nonces, it was time to solve the mystery.

\begin{minted}{bash}
$ pip install mersenne-twister-predictor
$ cat solution.py
import random

from mt19937predictor import MT19937Predictor

predictor = MT19937Predictor()
nonces = [
# THE NONCES HE DUMPED BEFORE
]

for i in range(624):
    predictor.setrandbits(nonces[i], 64)

while True:
    r2 = predictor.getrandbits(64)
    if r2 in nonces:
        print ("Value %d found in %d" % (r2, nonces.index(r2)))
    else:
        print("Break")
        break;

for i in range(5):
    print(hex(predictor.getrandbits(64)))
$ python solution.py
<snip>
\end{minted}

The answer was 57066318f32f729d. Grinch smiled.
